NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-14 paper/Chapters/Chapter3.tex
after last meeting with Luigi

		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means}}\\

>>>>

		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from $\chi^2$ test for categorical variables, and one-way ANOVA comparing the means}}\\

### 2018-08-14 paper/Chapters/Chapter4.tex
after last meeting with Luigi

Using multilevel LCA as a novel technique, and the NDNS RP dietary database, this project examined carbohydrate eating temporal patterns in the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently. Among all of the dietary diaries, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained for across the hours of day (high carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low carbohydrate day); and 3) always having lunch and dinner day (regular meals day).

>>>>

Using multilevel LCA as a novel technique, and the NDNS RP dietary database, this project examined carbohydrate eating temporal patterns in the day level, based on which, individual level carbohydrate eating patterns were also defined subsequently. Among the dietary diaries collected, there were three distinct latent classes specifically for carbohydrate intake: 1) high probabilities of having high carbohydrate contained food across the hours of day (high carbohydrate day); 2) low carbohydrate food dominant through out the hours of day (low carbohydrate day); and 3) always having lunch and dinner day (regular meals day).
